### 2008-12-10 articles/2009/geoinformatics/article.tex
added a latex example environment to start
git-svn-id: https://svn.osgeo.org/qgis/trunk@9766 c8812cc2-4d05-0410-92ff-de0c093fc19c

\section{Section}
\pagenumbering{arabic}
\setcounter{page}{1}

Einen guten Forscher erkennt man daran, dass er alle Hintergruende erforscht.
Ich, Prof. Lactosius, bin natuerlich ein guter Forscher. Deshalb habe ich auch
die Quelle der Schulmilch, die Kuehe, gruendlich erforscht.

\subsection{Subsection}

Ich weiss schon, was ihr jetzt sagen werdet. Jeder weiss, wie eine Kuh aussieht.
Aber auch bei den Kuehen habe ich kleine und groessere Unterschiede entdeckt.
Also los, folgt mir ins Land der Kuehe.

\begin{figure}[h]
   \begin{center}
   \caption{Example Figure}\label{fig:example-figure}\smallskip
   \includegraphics[clip=true]{test-image}
\end{center}
\end{figure}

\minisec{Minisec}

...

### 2009-01-05 articles/2009/geoinformatics/article.tex
started with the article
git-svn-id: https://svn.osgeo.org/qgis/trunk@9926 c8812cc2-4d05-0410-92ff-de0c093fc19c

@@
-\section{Section}
+\section{Quantum GIS 1.0.0}
 \pagenumbering{arabic}
@@
 
-Einen guten Forscher erkennt man daran, dass er alle Hintergruende erforscht.
-Ich, Prof. Lactosius, bin natuerlich ein guter Forscher. Deshalb habe ich auch
-die Quelle der Schulmilch, die Kuehe, gruendlich erforscht.
+Quantum GIS (QGIS) is a cross-platform (GNU/Linux, MS Windows, Mac OSX) open
+source application with a growing number of common GIS features and
+functions. QGIS is licensed under the GNU General Public License and an
+official member project of the Open Source Geospatial Foundation (OSGeo). The
+current official version is 1.0.0, aka "Kore" and was released on January 05,
+2009.
 
-\subsection{Subsection}
+\subsection{History}
 
-Ich weiss schon, was ihr jetzt sagen werdet. Jeder weiss, wie eine Kuh aussieht.
-Aber auch bei den Kuehen habe ich kleine und groessere Unterschiede entdeckt.
-Also los, folgt mir ins Land der Kuehe.
+The idea for Quantum GIS was born in the beginning of 2002 when Gary Sherman
+began looking for a GIS viewer for Linux that was fast and supported a wide
+range of data stores. That, coupled with an interest in coding a GIS
+application led to the creation of the project. In the beginning Quantum GIS
+was established as a project on SourceForge in June 2002 with the first,
+mostly non-functioning release on July 19, 2002. This first release supported
+only PostGIS layers.
+
+Within the last 7 years, the project
+
+\subsection{QGIS Community}
 
@@
    \begin{center}
-   \caption{Example Figure}\label{fig:example-figure}\smallskip
-   \includegraphics[clip=true]{test-image}
+   \caption{QGIS Community Map}\label{fig:community-map}\smallskip
+   \includegraphics[clip=true]{community-map}
 \end{center}
@@
 
-\minisec{Minisec}
+\subsection{Functionality}
 
-...
+\subsection{Development}
+
+\subsection{Conclusion}
+
+\minisec{Authors}
+
+The authors of this article are QGIS Project Steering Committee Members:
+
+Otto Dassau <dassau@nature-consult.de>  
+\\Gary Sherman <sherman@mrcc.com>
+\\Tim Sutton <tim@linfinity.com>
+\\Marco Hugentobler <marco.hugentobler@karto.baug.ethz.ch>
+\\Paolo Cavallini <cavallini@faunalia.it>
+
+\minisec{Links}
+
+For more information, have a look at the following website:
+
+Quantum GIS website: http://qgis.osgeo.org

### 2009-01-06 articles/2009/geoinformatics/article.tex
added some text from VisualChangelog1.0
git-svn-id: https://svn.osgeo.org/qgis/trunk@9931 c8812cc2-4d05-0410-92ff-de0c093fc19c

@@
-\section{Quantum GIS 1.0.0}
+\section{Quantum GIS 1.0}
 \pagenumbering{arabic}
@@
 
-Quantum GIS (QGIS) is a cross-platform (GNU/Linux, MS Windows, Mac OSX) open
-source application with a growing number of common GIS features and
-functions. QGIS is licensed under the GNU General Public License and an
-official member project of the Open Source Geospatial Foundation (OSGeo). The
-current official version is 1.0.0, aka "Kore" and was released on January 05,
-2009.
+Quantum GIS (QGIS) is a user friendly Open Source Geographic Information
+System (GIS), licensed under the GNU General Public License, that runs on
+GNU/Linux, Unix, Mac OSX, and MS Windows. QGIS supports numerous vector, 
+raster, and database formats and provides a wide variety of plugins to do 
+things like display tracks from your GPS, edit and analyse vector geometries 
+and attribute data, compose print layouts, and much more.
 
-\subsection{History}
+\subsection{History and Facts}
 
-The idea for Quantum GIS was born in the beginning of 2002 when Gary Sherman
-began looking for a GIS viewer for Linux that was fast and supported a wide
-range of data stores. That, coupled with an interest in coding a GIS
-application led to the creation of the project. In the beginning Quantum GIS
-was established as a project on SourceForge in June 2002 with the first,
-mostly non-functioning release on July 19, 2002. This first release supported
-only PostGIS layers.
+QGIS began life in February of 2002, with the first release in June of the
+same year. The initial goal was to create a viewer for PostGIS data that ran
+on Linux. From those humble beginnings, QGIS has become a true cross-platform
+application that runs on all major versions of unix, Linux, as well as Mac
+and Windows. It supports editing and map composition as well as integration
+with GRASS to provide powerful GIS capability.
 
-Within the last 7 years, the project
+QGIS 1.0, released in January 2009 provides a stable API from which you can
+develop custom solutions in Python or C++. Even though 1.0 is fresh, there
+are a number of exciting developments underway in both the core application
+and plugins.
 

### 2009-01-12 articles/2009/geoinformatics/article.tex
more updates
git-svn-id: https://svn.osgeo.org/qgis/trunk@9963 c8812cc2-4d05-0410-92ff-de0c093fc19c

@@
 
-Quantum GIS (QGIS) is a user friendly Open Source Geographic Information
-System (GIS), licensed under the GNU General Public License, that runs on
-GNU/Linux, Unix, Mac OSX, and MS Windows. QGIS supports numerous vector, 
-raster, and database formats and provides a wide variety of plugins to do 
-things like display tracks from your GPS, edit and analyse vector geometries 
-and attribute data, compose print layouts, and much more.
+Quantum GIS (QGIS) is a user friendly Geographic Information System (GIS) and
+an official project of the Open Source Geospatial Foundation (OSGeo). QGIS is
+licensed under the GNU General Public License.
 
-\subsection{History and Facts}
+\minisec{History}
 
@@
 same year. The initial goal was to create a viewer for PostGIS data that ran
-on Linux. From those humble beginnings, QGIS has become a true cross-platform
-application that runs on all major versions of unix, Linux, as well as Mac
-and Windows. It supports editing and map composition as well as integration
-with GRASS to provide powerful GIS capability.
+on GNU/Linux. From those humble beginnings, QGIS has become a true
+cross-platform application that runs on all major versions of unix,
+GNU/Linux, as well as Mac OS and MS Windows. It supports numerous vector,
+raster, and database formats and provides a wide variety of core and external
+geoprocessing functionalities.
 
-QGIS 1.0, released in January 2009 provides a stable API from which you can
-develop custom solutions in Python or C++. Even though 1.0 is fresh, there
-are a number of exciting developments underway in both the core application
-and plugins.
+\subsection{QGIS is Open Source}
 
-\subsection{QGIS Community}
+The QGIS project is carried out largely by a group of developers,
+translators, documenters, release helpers, bug reporters and promoters. All
+these volunteers together with a large number of users make up the QGIS
+comunity, which in time has built up a comprehensive, valuable and useful
+code and documentation base free to use and improve for everybody.
 
@@
 \subsection{Functionality}
+
+Current QGIS 1.0, released in January 2009, provides a stable API from which
+you can develop custom solutions in Python or C++. Even though 1.0 is fresh,
+there are a number of exciting developments underway in both the core
+application and plugins. QGIS offers a growing number of common GIS
+functionalities provided by core features and plugins. This includes to:
+
+\begin{figure}[h]
+   \begin{center}
+   \caption{Quantum GIS 1.0.0 'Kore'}\label{fig:qgis10}\smallskip
+   \includegraphics[clip=true, width=\textwidth]{qgis10}
+\end{center}
+\end{figure}
+
+\begin{itemize}
+\item view and overlay vector and raster layer in different formats and
+projections without conversion to an internal or common format. Supported are
+PostgreSQL/PostGIS, GDAL/OGR supported vector and raster layers such as ESRI
+Shapefile, MapInfo, GML, GeoTiff or Erdas Img., GRASS locations, and
+OGC-compliant WMS and WFS;
+\item interactively explore data, including features such as on the fly
+(OTF) projection, identify/select geometries, view, select and search
+attributes, label features, change vector and raster symbology; 
+\item compose print layouts adding map canvas, legend, scalebar, images and
+text lables in a print composer plugin;
+\item create, edit, manage and export vector layers into several formats.
+Raster layer have to be imported into GRASS GIS to be edited and
+exported. 
+\item perform spatial geoprocessing on PostgreSQL/PostGIS and other OGR
+supported vector layers including overlay, buffer, sampling, geometry and
+database management. The integrated GRASS Plugin allows to include the
+complete GRASS functionality of more than 300 modules.
+\end{itemize}
+
+\subsection{Plugins}
+
+QGIS can be adapted to your special needs with the help of an extensible
+plugin architecture. It provides libraries that can be used to create
+QGIS plugins or even new applications with C++ or Python. Most Python plugins
+are managed in external repositories, and can be easily installed using the
+Python Plugin Installer.
+
+\begin{figure}[h]
+   \begin{center}
+   \caption{QGIS Python Plugin Installer}\label{fig:python-plugin}\smallskip
+   \includegraphics[clip=true, width=\textwidth]{python-plugin-installer}
+\end{center}
+\end{figure}
 
@@
 
-Quantum GIS website: http://qgis.osgeo.org
+Quantum GIS project: http://qgis.osgeo.org
+\\Open Source Geospatial Foundation: http://www.osgeo.org

### 2009-01-19 articles/2009/geoinformatics/article.tex
small change
git-svn-id: https://svn.osgeo.org/qgis/trunk@9964 c8812cc2-4d05-0410-92ff-de0c093fc19c
small updates
git-svn-id: https://svn.osgeo.org/qgis/trunk@9981 c8812cc2-4d05-0410-92ff-de0c093fc19c

@@
 
-\subsection{QGIS is Open Source}
+\subsection{QGIS Open Source Community}
 
-The QGIS project is carried out largely by a group of developers,
-translators, documenters, release helpers, bug reporters and promoters. All
-these volunteers together with a large number of users make up the QGIS
-comunity, which in time has built up a comprehensive, valuable and useful
-code and documentation base free to use and improve for everybody.
+The QGIS project is Open Source and carried out largely by a group of
+developers, translators, documenters, release helpers, bug reporters, and
+promoters. All these volunteers together with a large number of users make up
+the QGIS comunity, which in time has built up a comprehensive, valuable and
+useful code and documentation base free to use and improve for everybody.
 
@@
 \end{figure}
+
+There are several possibilities to get in contact with the QGIS project. 
+A prefered way is is by joining the qgis-users mailing list or the QGIS Forum.
 
@@
 
-\subsection{Conclusion}
+\subsection{Perspective / Conclusion}
 

### 2009-01-24 articles/2009/geoinformatics/article.tex
a few updates
git-svn-id: https://svn.osgeo.org/qgis/trunk@10008 c8812cc2-4d05-0410-92ff-de0c093fc19c

@@
 an official project of the Open Source Geospatial Foundation (OSGeo). QGIS is
-licensed under the GNU General Public License.
+written in C++ and Python with a QT based GUI. It is licensed inder the GNU
+General Public License (GPL).
 
@@
 
-\subsection{Plugins}
+\subsection{Plugin Architecture}
 
-QGIS can be adapted to your special needs with the help of an extensible
+QGIS can be customized to your special needs with the help of an extensible
 plugin architecture. It provides libraries that can be used to create
-QGIS plugins or even new applications with C++ or Python. Most Python plugins
-are managed in external repositories, and can be easily installed using the
-Python Plugin Installer.
+QGIS plugins or even new applications with C++ or Python.
+
+\subsection{External Python Plugin Repositories}
+
+Most Python plugins are managed in external repositories, and can be easily
+installed using the Python Plugin Installer.
 

### 2009-01-25 articles/2009/geoinformatics/article.tex
added more text
git-svn-id: https://svn.osgeo.org/qgis/trunk@10013 c8812cc2-4d05-0410-92ff-de0c093fc19c

--- 2009-01-12 articles/2009/geoinformatics/article.tex
@@
 
-Quantum GIS (QGIS) is a user friendly Geographic Information System (GIS) and
-an official project of the Open Source Geospatial Foundation (OSGeo). QGIS is
-licensed under the GNU General Public License.
+Quantum GIS (QGIS) is a user friendly Geographic Information System (GIS).
+It is written in C++ and Python with a QT based GUI. It is licensed under the
+GNU General Public License (GPL) and an official project of the Open Source
+Geospatial Foundation (OSGeo). The current stable version 1.0 was released in
+January 2009.
 
@@
 
-QGIS began life in February of 2002, with the first release in June of the
-same year. The initial goal was to create a viewer for PostGIS data that ran
-on GNU/Linux. From those humble beginnings, QGIS has become a true
-cross-platform application that runs on all major versions of unix,
+The QGIS project started in February of 2002, with the first release in June
+of the same year. The initial goal was to create a viewer for PostGIS data
+that ran on GNU/Linux. From those beginnings, QGIS has become a true
+cross-platform application that runs on all major versions of Unix,
 GNU/Linux, as well as Mac OS and MS Windows. It supports numerous vector,
@@
 
-\subsection{QGIS is Open Source}
+\subsection{QGIS Open Source Community}
 
-The QGIS project is carried out largely by a group of developers,
-translators, documenters, release helpers, bug reporters and promoters. All
-these volunteers together with a large number of users make up the QGIS
-comunity, which in time has built up a comprehensive, valuable and useful
-code and documentation base free to use and improve for everybody.
+The QGIS project is carried out largely by a group of dedicated developers,
+translators, documenters, release helpers, bug reporters, and promoters. It
+is managed by the Project Steering Committee (PSC), a five member committee
+providing technical guidance, community liason, release management, and
+financial/marketing activities. The work of the QGIS project process is
+spread between numerous people who each have a specific area of
+resposibility.
+
+All these volunteers together with a large number of users make up the
+world-wide QGIS comunity, which in time has built up a comprehensive,
+valuable and useful code and documentation base free to use and improve for
+everybody.
 
@@
    \caption{QGIS Community Map}\label{fig:community-map}\smallskip
-   \includegraphics[clip=true]{community-map}
+   \includegraphics[clip=true, width=10cm]{community-map}
 \end{center}
@@
 
+With community platforms such as website, wiki, and blog the QGIS project
+provides latest news, release, usage, and development information and also
+allows own contributions after subscription. A prefered first step to contact
+other users for discussions of QGIS in general, as well as specific questions
+regarding its installation and use is by joining the qgis-user mailing list,
+the QGIS Forum or the Internet Relay Chat (IRC).
+
 \subsection{Functionality}
 
-Current QGIS 1.0, released in January 2009, provides a stable API from which
-you can develop custom solutions in Python or C++. Even though 1.0 is fresh,
-there are a number of exciting developments underway in both the core
-application and plugins. QGIS offers a growing number of common GIS
-functionalities provided by core features and plugins. This includes to:
+QGIS offers a growing number of common GIS functionalities provided by core
+features and plugins. They are presented in a friendly graphical user
+interface, clearly seperated in menu bar, tool bar, status bar, map view,
+overview, and map legend (see Figure~\ref{fig:qgis10}).
 
@@
 \end{figure}
+
+The menu and tool bar give access to all QGIS features and at a glance
+provide following features:
 
@@
 
-\subsection{Plugins}
+\subsection{Plugin Architecture}
 
-QGIS can be adapted to your special needs with the help of an extensible
-plugin architecture. It provides libraries that can be used to create
-QGIS plugins or even new applications with C++ or Python. Most Python plugins
-are managed in external repositories, and can be easily installed using the
-Python Plugin Installer.
+QGIS has been designed with a plugin architecture and therefore new
+customized features and functions can easily be added to the application.
+Many of the features in QGIS are actually implemented as core or external
+plugins.
+
+\textbf{Core Plugins} are maintained by the QGIS Development Team. They are
+written in C++ or Python, are automatically part of every QGIS distribution
+and can be loaded with the Plugin Manager. There are currently 17 core
+plugins available, such as GRASS GIS integration (See
+Figure~\ref{fig:grass-plugin}), Georeferencer, Mapserver Export, Shapefile to
+PostGIS Import Tool, OGR Layer Converter, GPS Tools, Add Delimited Text Layer
+or WFS support:
+
+\begin{figure}[h]
+   \begin{center}
+   \caption{QGIS Core Plugin (GRASS GIS Integration)}
+    \label{fig:grass-plugin}\smallskip
+   \includegraphics[clip=true, width=14cm]{grass-plugin}
+\end{center}
+\end{figure}
+
+\textbf{External Plugins} are all written in Python. They are stored in
+an official, external repository and maintained by the individual author. The
+user can easily add those Plugins to QGIS with the Python Plugin Installer
+(See Figure~\ref{fig:python-plugin}).
 
@@
 
-\subsection{Conclusion}
+QGIS 1.0 provides a stable API from which custom solutions in Python or C++
+can be developed. Even though 1.0 is pretty fresh, there are already a number
+of exciting developments underway in both the core application and plugins.
+
+\subsection{Perspective / Conclusion}
 
@@
 
-Quantum GIS project: http://qgis.osgeo.org
+Quantum GIS project: http://qgis.org
+\\QGIS Forum: http://forum.qgis.org
+\\QGIS Blog: http://blog.qgis.org
+\\QGIS User Mailing List: http://lists.osgeo.org/mailman/listinfo/qgis-user
+\\QGIS IRC: Channel \#qgis port 6667 at irc.freenode.net
 \\Open Source Geospatial Foundation: http://www.osgeo.org

### 2009-01-26 articles/2009/geoinformatics/article.tex
Initial edits by Tim
git-svn-id: https://svn.osgeo.org/qgis/trunk@10015 c8812cc2-4d05-0410-92ff-de0c093fc19c

@@
 Quantum GIS (QGIS) is a user friendly Geographic Information System (GIS).
-It is written in C++ and Python with a QT based GUI. It is licensed under the
+It is written in C++ and Python with a Qt4 based GUI. It is licensed under the
 GNU General Public License (GPL) and an official project of the Open Source
@@
 
-The QGIS project is carried out largely by a group of dedicated developers,
-translators, documenters, release helpers, bug reporters, and promoters. It
+The QGIS project is the work of a group of dedicated developers,
+translators, documenters, release helpers, bug reporters, and promoters. Their 
+contributions are mainly on a voluntary basis, except in a few cases where 
+contributors are able to work on QGIS as part of their daily work. QGIS 
 is managed by the Project Steering Committee (PSC), a five member committee
@@
 spread between numerous people who each have a specific area of
-resposibility.
+resposibility, and ad hoc contributors.
 
-All these volunteers together with a large number of users make up the
-world-wide QGIS comunity, which in time has built up a comprehensive,
-valuable and useful code and documentation base free to use and improve for
-everybody.
+These volunteers together with a large number of users make up the
+world-wide QGIS comunity. Over time their efforts have resulted in a comprehensive,
+valuable and useful code and documentation base which is free for everyone 
+to use and improve on.
 
@@
 
-With community platforms such as website, wiki, and blog the QGIS project
-provides latest news, release, usage, and development information and also
-allows own contributions after subscription. A prefered first step to contact
-other users for discussions of QGIS in general, as well as specific questions
-regarding its installation and use is by joining the qgis-user mailing list,
-the QGIS Forum or the Internet Relay Chat (IRC).
+With community platforms such as our website, wiki, forums and blog the QGIS project
+provides latest news, release, usage, and development information. In most cases 
+these community web sites permit user contributions after registering. 
+The QGIS-user mailing, forum and Internet Relay Chat (IRC) provide a valuable interface 
+with other users and for discussions of QGIS in general. In the spirit of open 
+process and sharing knowledge, contacting developers directly instead of going through 
+these community based avenues of communication is frowned apon.
 
@@
 
-QGIS offers a growing number of common GIS functionalities provided by core
+QGIS offers a growing number of common GIS functionality provided by core
 features and plugins. They are presented in a friendly graphical user
-interface, clearly seperated in menu bar, tool bar, status bar, map view,
+interface, clearly seperated into a menu bar, tool bars, status bar, map view,
 overview, and map legend (see Figure~\ref{fig:qgis10}).
@@
 
-The menu and tool bar give access to all QGIS features and at a glance
+The menu and tool bars give access to all QGIS features and at a glance
 provide following features:
@@
 \\Gary Sherman <sherman@mrcc.com>
-\\Tim Sutton <tim@linfinity.com>
+\\Tim Sutton <tim@linfiniti.com>
 \\Marco Hugentobler <marco.hugentobler@karto.baug.ethz.ch>

### 2009-01-27 articles/2009/geoinformatics/article.tex
more text and figures
git-svn-id: https://svn.osgeo.org/qgis/trunk@10032 c8812cc2-4d05-0410-92ff-de0c093fc19c

@@
 
-\subsection{Functionality}
+\subsection{Graphical User Interface}
 
-QGIS offers a growing number of common GIS functionality provided by core
-features and plugins. They are presented in a friendly graphical user
-interface, clearly seperated into a menu bar, tool bars, status bar, map view,
-overview, and map legend (see Figure~\ref{fig:qgis10}).
+Working with QGIS is simple and intuitive as you are presented with a
+modern and friendly graphical user interface (GUI) based on QT4. All
+functionalities are clearly seperated (see Figure~\ref{fig:qgis10}).
 
@@
    \caption{Quantum GIS 1.0.0 'Kore'}\label{fig:qgis10}\smallskip
-   \includegraphics[clip=true, width=\textwidth]{qgis10}
+   \includegraphics[clip=true, width=12cm]{qgis10}
 \end{center}
@@
 
-The menu and tool bars give access to all QGIS features and at a glance
-provide following features:
+A \textbf{menu bar} provides access to QGIS features using a standard
+hierarchical menu, with icons of the corresponding tools as they appear on
+the tool bar and with keyboard shortcuts. The \textbf{tool bar} icons provide
+direct access to functions of the menu bar, plus additional tools for
+interacting with the map view. To make the GUI appear clearer, tool bar icons
+can be switched on and off. The 'business end' of QGIS is the \textbf{map
+view}. Various operations can be performed on the map, such as pan, zoom-in,
+zoom-out, select or query. It is tightly bound to the \textbf{map legend},
+where layer visibility is managed and set to a z-order, meaning layers
+listed nearer the top of the legend are drawn over layers listed lower down.
+The \textbf{map overview} area provides a full extent view of selected layers
+with a rectangle showing the current map extent in the map view. And the
+\textbf{status bar} finally shows the current mouse pointer position in map
+coordinates, view extents of the map view, the progress of rendering or
+analysis activities, the current map scale depending on the defined
+Coordinate Reference System (CRS) and information about available external
+plugin updates.
+
+\subsection{Functionality}
+
+QGIS offers a growing number of common GIS functionality provided by core
+features and plugins and at a glance provide following features:
 
@@
 \end{itemize}
+
+\begin{figure}[h]
+   \begin{center}
+   \caption{QGIS Geoprocessing Tools}
+    \label{fig:geoprocessing}\smallskip
+   \includegraphics[clip=true, width=8cm]{geoprocessing}
+\end{center}
+\end{figure}
 
@@
 
-\textbf{External Plugins} are all written in Python. They are stored in
-an official, external repository and maintained by the individual author. The
-user can easily add those Plugins to QGIS with the Python Plugin Installer
-(See Figure~\ref{fig:python-plugin}).
+\textbf{External Plugins} are all written in Python and devided into official
+and user contributed plugins. The user can easily add those Plugins to QGIS
+with the Python Plugin Installer (See Figure~\ref{fig:python-plugin}).
+
+\begin{itemize}
+\item \textbf{Official} external python plugins are stored in an official,
+moderated repository at \url{http://pyqgis.org/repo/official} as part of the
+official QGIS release and maintained by the individual author.
+\item \textbf{User-Contributed} external python plugins are stored in an
+unofficial repository at \url{http://pyqgis.org/repo/contributed} and contain
+plugins that are not yet mature enough but on the way to the official
+repository.
+\end{itemize}
+
+Beside these two respositories a few QGIS developers provide and maintain
+their own repositories. They can be added to the repository list of the
+Python Plugin Installer.
 
@@
    \caption{QGIS Python Plugin Installer}\label{fig:python-plugin}\smallskip
-   \includegraphics[clip=true, width=\textwidth]{python-plugin-installer}
+   \includegraphics[clip=true, width=14cm]{python-plugin-installer}
 \end{center}

### 2009-01-29 articles/2009/geoinformatics/article.tex
Some text for the development section
git-svn-id: https://svn.osgeo.org/qgis/trunk@10041 c8812cc2-4d05-0410-92ff-de0c093fc19c

@@
 
-QGIS 1.0 provides a stable API from which custom solutions in Python or C++
-can be developed. Even though 1.0 is pretty fresh, there are already a number
-of exciting developments underway in both the core application and plugins.
+%QGIS 1.0 provides a stable API from which custom solutions in Python or C++
+%can be developed. Even though 1.0 is pretty fresh, there are already a number
+%of exciting developments underway in both the core application and plugins.
+
+As QGIS is open source software, it is possible to participate in development process and also to write new applications that use the libraries of the QGIS project.
+Development with QGIS can be done either in the existing classes of QGIS, as plugin extensions or in the form of custom applications that make use of the QGIS libraries.
+As a general note all code in QGIS is licensed under the GNU GPL.
+That means that for all three cases, published software must be distributed under the terms of the GPL too.
+QGIS 1.0 provides a stable API such that changes to developed plugins and applications will only be necessary for version 2 of QGIS.
+
+\subsubsection{Development in the core classes of QGIS}
+Changes in the already existing classes may be placed as patches at the bug tracker of the QGIS project (https://trac.osgeo.org/qgis/).
+The code maintainers of the QGIS project, each responsible for a certain part of the code base, regularly check the tracker.
+
+\subsubsection{Development of extensions as C++ or Python plugins}
+There is a plugin interface that allows extensions to access the running QGIS instance and to use and extend the objects in the core of QGIS.
+Plugins may be written in C++ or in Python.
+The QGIS documentation contains simple examples for both such that it is straightforward to start with plugin programming.
+
+\subsubsection{Custom applications that use the QGIS libaries}
+It is also possible to write new applications that provide its own user interface and use the QGIS core library for the GIS logic, data access and map rendering.
+
+An example for this approach is the QGIS mapserver project that provides a WMS compatible mapserver on top of the QGIS core library.
+This software has not a graphical user interface.
+It is a FastCGI application that waits until called by a webserver.
+It parses the request parameters and uses QGIS to render a map into an offscreen buffer.
+The content is then returned as binary image back to the client.
+
+Another context where this approach would make sense is to provide a mapping application for mobile devices.
+Applications for mobile devices usually need different user interfaces compared to applications for desktop computers and laptops.
+Still those applications could use the QGIS libraries as a GIS backend.
 

### 2009-01-30 articles/2009/geoinformatics/article.tex
a few blanks removed (just a test)
git-svn-id: https://svn.osgeo.org/qgis/trunk@10042 c8812cc2-4d05-0410-92ff-de0c093fc19c
Added line wrapping since its easier to diff changes in shorter lines
git-svn-id: https://svn.osgeo.org/qgis/trunk@10055 c8812cc2-4d05-0410-92ff-de0c093fc19c
Edits from proof read through
git-svn-id: https://svn.osgeo.org/qgis/trunk@10056 c8812cc2-4d05-0410-92ff-de0c093fc19c

@@
 contributions are mainly on a voluntary basis, except in a few cases where 
-contributors are able to work on QGIS as part of their daily work. QGIS 
+contributors are able to contribute to QGIS as part of their daily work. QGIS 
 is managed by the Project Steering Committee (PSC), a five member committee
@@
 spread between numerous people who each have a specific area of
-resposibility, and ad hoc contributors.
+resposibility, and ad-hoc contributors.
 
@@
 valuable and useful code and documentation base which is free for everyone 
-to use and improve on.
+to use and improve apon.
 
@@
 With community platforms such as our website, wiki, forums and blog the QGIS project
-provides latest news, release, usage, and development information. In most cases 
+provides current news, release, usage, and development information. In most cases 
 these community web sites permit user contributions after registering. 
@@
 modern and friendly graphical user interface (GUI) based on QT4. All
-functionalities are clearly seperated (see Figure~\ref{fig:qgis10}).
+functions are clearly separated (see Figure~\ref{fig:qgis10}).
 
@@
 written in C++ or Python, are automatically part of every QGIS distribution
-and can be loaded with the Plugin Manager. There are currently 17 core
-plugins available, such as GRASS GIS integration (See
+and can be enabled with the Plugin Manager. There are currently 17 core
+plugins available, including GRASS GIS integration (See
 Figure~\ref{fig:grass-plugin}), Georeferencer, Mapserver Export, Shapefile to
 PostGIS Import Tool, OGR Layer Converter, GPS Tools, Add Delimited Text Layer
-or WFS support:
+and WFS support.
 
@@
 
-\textbf{External Plugins} are all written in Python and devided into official
+\textbf{External Plugins} are all written in Python and divided into official
 and user contributed plugins. The user can easily add those Plugins to QGIS
@@
 moderated repository at \url{http://pyqgis.org/repo/official} as part of the
-official QGIS release and maintained by the individual author.
+official QGIS release and maintained by their respective author.
 \item \textbf{User-Contributed} external python plugins are stored in an
@@
 
-Beside these two respositories a few QGIS developers provide and maintain
-their own repositories. They can be added to the repository list of the
+Beside these two respositories a number of QGIS developers provide and maintain
+their own repositories. These can be added to the repository list of the
 Python Plugin Installer.
@@
 
-As QGIS is open source software, it is possible to participate in development process and also to write new applications that use the libraries of the QGIS project.
-Development with QGIS can be done either in the existing classes of QGIS, as plugin extensions or in the form of custom applications that make use of the QGIS libraries.
-As a general note all code in QGIS is licensed under the GNU GPL.
-That means that for all three cases, published software must be distributed under the terms of the GPL too.
-QGIS 1.0 provides a stable API such that changes to developed plugins and applications will only be necessary for version 2 of QGIS.
+Since QGIS is open source software, it is possible to participate in the development
+process and also to write new applications that use the libraries of the QGIS
+project. Development with QGIS can be done either in the existing classes of
+QGIS, as plugin extensions or in the form of custom applications that make use
+of the QGIS libraries. As a general note all code in QGIS is licensed under the
+GNU GPL. That means that for all three cases, published software must be
+distributed under the terms of the GPL too. QGIS 1.0 provides a stable API which 
+provides an assurance that plugins and applications developed against the 1.0 API 
+will work against future releases in the 1.X release series.
 
 \subsubsection{Development in the core classes of QGIS}
-Changes in the already existing classes may be placed as patches at the bug tracker of the QGIS project (https://trac.osgeo.org/qgis/).
-The code maintainers of the QGIS project, each responsible for a certain part of the code base, regularly check the tracker.
+Changes to existing classes may be submitted as patches using QGIS Project bug
+tracker (https://trac.osgeo.org/qgis/). The code maintainers of the QGIS
+project, each responsible for a certain part of the code base, regularly check
+the tracker.
 
 \subsubsection{Development of extensions as C++ or Python plugins}
-There is a plugin interface that allows extensions to access the running QGIS instance and to use and extend the objects in the core of QGIS.
-Plugins may be written in C++ or in Python.
-The QGIS documentation contains simple examples for both such that it is straightforward to start with plugin programming.
+There is a plugin interface that allows extensions to access the running QGIS
+instance and to use and extend the objects in the core of QGIS. Plugins may be
+written in C++ or in Python. The QGIS documentation contains simple examples
+for both programming languages making it straightforward to start with plugin 
+programming.
 
 \subsubsection{Custom applications that use the QGIS libaries}
-It is also possible to write new applications that provide its own user interface and use the QGIS core library for the GIS logic, data access and map rendering.
+It is also possible to write new applications that provide their own user
+interface and use the QGIS core library for the GIS logic, data access and map
+rendering.
 
-An example for this approach is the QGIS mapserver project that provides a WMS compatible mapserver on top of the QGIS core library.
-This software has not a graphical user interface.
-It is a FastCGI application that waits until called by a webserver.
-It parses the request parameters and uses QGIS to render a map into an offscreen buffer.
-The content is then returned as binary image back to the client.
+An example using this approach is the QGIS mapserver project that provides a WMS
+compatible mapserver on top of the QGIS core library. This software has no 
+graphical user interface. It is a FastCGI application that waits until called
+by a webserver. It parses the request parameters and uses QGIS to render a map
+into an offscreen buffer. The content is then returned as binary image back to
+the client.
 
-Another context where this approach would make sense is to provide a mapping application for mobile devices.
-Applications for mobile devices usually need different user interfaces compared to applications for desktop computers and laptops.
-Still those applications could use the QGIS libraries as a GIS backend.
+Another context where this approach would make sense is to provide a mapping
+application for mobile devices. Applications for mobile devices usually need
+different user interfaces to desktop computers applications and
+laptops. The QGIS libraries offer the potential to be used as a GIS backend for 
+applications targeted to mobile devices.
 

### 2009-01-31 articles/2009/geoinformatics/article.tex
Typos and some more text in the plugin section
git-svn-id: https://svn.osgeo.org/qgis/trunk@10057 c8812cc2-4d05-0410-92ff-de0c093fc19c

@@
 cross-platform application that runs on all major versions of Unix,
-GNU/Linux, as well as Mac OS and MS Windows. It supports numerous vector,
+GNU/Linux, as well as Mac OSX and MS Windows. It supports numerous vector,
 raster, and database formats and provides a wide variety of core and external
@@
 spread between numerous people who each have a specific area of
-resposibility, and ad-hoc contributors.
+responsibility, and ad-hoc contributors.
 
@@
 valuable and useful code and documentation base which is free for everyone 
-to use and improve apon.
+to use and improve upon.
 
@@
 direct access to functions of the menu bar, plus additional tools for
-interacting with the map view. To make the GUI appear clearer, tool bar icons
+interacting with the map view. To make the GUI appear simpler, tool bar icons
 can be switched on and off. The 'business end' of QGIS is the \textbf{map
@@
 PostgreSQL/PostGIS, GDAL/OGR supported vector and raster layers such as ESRI
-Shapefile, MapInfo, GML, GeoTiff or Erdas Img., GRASS locations, and
+Shapefile, MapInfo, GML, GeoTiff or Erdas Img., GRASS rasters, vectors, and locations, and
 OGC-compliant WMS and WFS;
@@
 Raster layer have to be imported into GRASS GIS to be edited and
-exported. 
+exported;
 \item perform spatial geoprocessing on PostgreSQL/PostGIS and other OGR
 supported vector layers including overlay, buffer, sampling, geometry and
-database management. The integrated GRASS Plugin allows to include the
-complete GRASS functionality of more than 300 modules.
+database management. The integrated GRASS Plugin allows to include the GRASS functionality of more than 300 modules.
 \end{itemize}
@@
    \begin{center}
-   \caption{QGIS Core Plugin (GRASS GIS Integration)}
+   \caption{One of the QGIS Core Plugin (GRASS GIS Integration)}
     \label{fig:grass-plugin}\smallskip
@@
 
-Since QGIS is open source software, it is possible to participate in the development
+Since QGIS is open source software, it is possible and encouraged to participate in the development
 process and also to write new applications that use the libraries of the QGIS
@@
 QGIS, as plugin extensions or in the form of custom applications that make use
-of the QGIS libraries. As a general note all code in QGIS is licensed under the
-GNU GPL. That means that for all three cases, published software must be
+of the QGIS libraries. All code in QGIS is licensed under the
+GNU GPL (\url{http://www.fsf.org/licensing/licenses/gpl.html}). That means that for all three cases, published software must be
 distributed under the terms of the GPL too. QGIS 1.0 provides a stable API which 
@@
 Changes to existing classes may be submitted as patches using QGIS Project bug
-tracker (https://trac.osgeo.org/qgis/). The code maintainers of the QGIS
+tracker (\url{https://trac.osgeo.org/qgis/}). The code maintainers of the QGIS
 project, each responsible for a certain part of the code base, regularly check
@@
 programming.
+The development of python plugins is especially fast and convenient.
+Simple plugins require only a few hours of development.
+As a result, an increasing number of users are contributing new plugins, of either specialized or general use.
 
@@
 
-An example using this approach is the QGIS mapserver project that provides a WMS
+An example using this approach is the QGIS mapserver project (\url{http://karlinapp.ethz.ch}) that provides a WMS
 compatible mapserver on top of the QGIS core library. This software has no 
@@
 
-Quantum GIS project: http://qgis.org
-\\QGIS Forum: http://forum.qgis.org
-\\QGIS Blog: http://blog.qgis.org
-\\QGIS User Mailing List: http://lists.osgeo.org/mailman/listinfo/qgis-user
-\\QGIS IRC: Channel \#qgis port 6667 at irc.freenode.net
-\\Open Source Geospatial Foundation: http://www.osgeo.org
+Quantum GIS project: \url{http://qgis.org}
+\\QGIS Forum: \url{http://forum.qgis.org}
+\\QGIS Blog: \url{http://blog.qgis.org}
+\\QGIS User Mailing List: \url{http://lists.osgeo.org/mailman/listinfo/qgis-user}
+\\QGIS IRC: Channel \#qgis port 6667 at \url{irc.freenode.net}
+\\Open Source Geospatial Foundation: \url{http://www.osgeo.org}

### 2009-01-31 articles/2009/geoinformatics/article.tex
More text
git-svn-id: https://svn.osgeo.org/qgis/trunk@10058 c8812cc2-4d05-0410-92ff-de0c093fc19c

@@
 is managed by the Project Steering Committee (PSC), a five member committee
-providing technical guidance, community liason, release management, and
+providing technical guidance, community liaison, release management, and
 financial/marketing activities. The work of the QGIS project process is
@@
 These volunteers together with a large number of users make up the
-world-wide QGIS comunity. Over time their efforts have resulted in a comprehensive,
+world-wide QGIS community. Over time their efforts have resulted in a comprehensive,
 valuable and useful code and documentation base which is free for everyone 
@@
 process and sharing knowledge, contacting developers directly instead of going through 
-these community based avenues of communication is frowned apon.
+these community based avenues of communication is frowned upon.
 
@@
 QGIS has been designed with a plugin architecture and therefore new
-customized features and functions can easily be added to the application.
+customised features and functions can easily be added to the application.
 Many of the features in QGIS are actually implemented as core or external
@@
 
-Beside these two respositories a number of QGIS developers provide and maintain
+Beside these two repositories a number of QGIS developers provide and maintain
 their own repositories. These can be added to the repository list of the
@@
 Simple plugins require only a few hours of development.
-As a result, an increasing number of users are contributing new plugins, of either specialized or general use.
+As a result, an increasing number of users are contributing new plugins, of either specialised or general use.
 
@@
 applications targeted to mobile devices.
+
+\subsection{Who uses QGIS}
+QGIS is now widely used by professionals, government and local agencies, universities and students, and amateurs alike, for a large variety of tasks, from simply viewing raster and vector data (especially useful is the capability to deal with PostGIS layers) to running complex and custom analyses through GRASS modules.
+Often is used to replace or integrate proprietary software, and several migrations have been accomplished or are underway, both in small and in large companies and public administrations.
+Among the hundreds of people that have attended courses on QGIS use, a common feeling is that the switch from proprietary software is painless, because many tasks and menus are very similar, and the interface is generally judged intuitive.
 

### 2009-01-31 articles/2009/geoinformatics/article.tex
Who uses qgis
git-svn-id: https://svn.osgeo.org/qgis/trunk@10059 c8812cc2-4d05-0410-92ff-de0c093fc19c

@@
 Often is used to replace or integrate proprietary software, and several migrations have been accomplished or are underway, both in small and in large companies and public administrations.
-Among the hundreds of people that have attended courses on QGIS use, a common feeling is that the switch from proprietary software is painless, because many tasks and menus are very similar, and the interface is generally judged intuitive.
+Among the hundreds of people that have attended courses on QGIS use, a common feeling is that the switch from proprietary software is painless, because many tasks and menus are very similar, and the interface is generally judged very intuitive.
+No doubt thanks to its free and open source licence, it is also used in some of the poorest countries, thus helping to reduce the world digital divde and bring more geoinformatic knowledge where local conditions are more difficult.
+Professional support is provided by several companies.
 

### 2009-01-31 articles/2009/geoinformatics/article.tex
misspell
git-svn-id: https://svn.osgeo.org/qgis/trunk@10060 c8812cc2-4d05-0410-92ff-de0c093fc19c

@@
 Among the hundreds of people that have attended courses on QGIS use, a common feeling is that the switch from proprietary software is painless, because many tasks and menus are very similar, and the interface is generally judged very intuitive.
-No doubt thanks to its free and open source licence, it is also used in some of the poorest countries, thus helping to reduce the world digital divde and bring more geoinformatic knowledge where local conditions are more difficult.
+No doubt thanks to its free and open source licence, it is also used in some of the poorest countries, thus helping to reduce the world digital divide and bring more geoinformatic knowledge where local conditions are more difficult.
 Professional support is provided by several companies.
@@
 
-The authors of this article are QGIS Project Steering Committee Members:
+The authors of this article are the QGIS Project Steering Committee Members:
 

### 2009-01-31 articles/2009/geoinformatics/article.tex
Adding more text to the geoinformatics article
git-svn-id: https://svn.osgeo.org/qgis/trunk@10070 c8812cc2-4d05-0410-92ff-de0c093fc19c

@@
 These volunteers together with a large number of users make up the
-world-wide QGIS community. Over time their efforts have resulted in a comprehensive,
+world-wide QGIS community. Over time their efforts have resulted in a
+comprehensive,
 valuable and useful code and documentation base which is free for everyone 
@@
 
-With community platforms such as our website, wiki, forums and blog the QGIS project
-provides current news, release, usage, and development information. In most cases 
+With community platforms such as our website, wiki, forums and blog the QGIS
+project
+provides current news, release, usage, and development information. In most
+cases 
 these community web sites permit user contributions after registering. 
-The QGIS-user mailing, forum and Internet Relay Chat (IRC) provide a valuable interface 
+The QGIS-user mailing, forum and Internet Relay Chat (IRC) provide a valuable
+interface 
 with other users and for discussions of QGIS in general. In the spirit of open 
-process and sharing knowledge, contacting developers directly instead of going through 
+process and sharing knowledge, contacting developers directly instead of going
+through 
 these community based avenues of communication is frowned upon.
@@
 PostgreSQL/PostGIS, GDAL/OGR supported vector and raster layers such as ESRI
-Shapefile, MapInfo, GML, GeoTiff or Erdas Img., GRASS rasters, vectors, and locations, and
+Shapefile, MapInfo, GML, GeoTiff or Erdas Img., GRASS rasters, vectors, and
+locations, and
 OGC-compliant WMS and WFS;
@@
 supported vector layers including overlay, buffer, sampling, geometry and
-database management. The integrated GRASS Plugin allows to include the GRASS functionality of more than 300 modules.
+database management. The integrated GRASS Plugin allows to easily access more
+than 260 GRASS modules, allowing complex GIS raster and vector analyses,
+including raster algebra, hydrological modelling, interpolating surfaces,
+network analyses, database operations, and much more.
 \end{itemize}
@@
 
-Since QGIS is open source software, it is possible and encouraged to participate in the development
+Since QGIS is open source software, it is possible and encouraged to participate
+in the development
 process and also to write new applications that use the libraries of the QGIS
@@
 of the QGIS libraries. All code in QGIS is licensed under the
-GNU GPL (\url{http://www.fsf.org/licensing/licenses/gpl.html}). That means that for all three cases, published software must be
-distributed under the terms of the GPL too. QGIS 1.0 provides a stable API which 
-provides an assurance that plugins and applications developed against the 1.0 API 
+GNU GPL (\url{http://www.fsf.org/licensing/licenses/gpl.html}). That means that
+for all three cases, published software must be
+distributed under the terms of the GPL too. QGIS 1.0 provides a stable API
+which 
+provides an assurance that plugins and applications developed against the 1.0
+API 
 will work against future releases in the 1.X release series.
@@
 for both programming languages making it straightforward to start with plugin 
-programming.
-The development of python plugins is especially fast and convenient.
-Simple plugins require only a few hours of development.
-As a result, an increasing number of users are contributing new plugins, of either specialised or general use.
+programming. The development of python plugins is especially fast and
+convenient. Simple plugins require only a few hours of development. As a result,
+an increasing number of users are contributing new plugins, of either
+specialised or general use.
 
@@
 
-An example using this approach is the QGIS mapserver project (\url{http://karlinapp.ethz.ch}) that provides a WMS
+An example using this approach is the QGIS mapserver project
+(\url{http://karlinapp.ethz.ch}) that provides a WMS
 compatible mapserver on top of the QGIS core library. This software has no 
@@
 \subsection{Who uses QGIS}
-QGIS is now widely used by professionals, government and local agencies, universities and students, and amateurs alike, for a large variety of tasks, from simply viewing raster and vector data (especially useful is the capability to deal with PostGIS layers) to running complex and custom analyses through GRASS modules.
-Often is used to replace or integrate proprietary software, and several migrations have been accomplished or are underway, both in small and in large companies and public administrations.
-Among the hundreds of people that have attended courses on QGIS use, a common feeling is that the switch from proprietary software is painless, because many tasks and menus are very similar, and the interface is generally judged very intuitive.
-No doubt thanks to its free and open source licence, it is also used in some of the poorest countries, thus helping to reduce the world digital divide and bring more geoinformatic knowledge where local conditions are more difficult.
+QGIS is now widely used by professionals, government and local agencies,
+universities and students, and amateurs alike, for a large variety of tasks,
+from simply viewing raster and vector data (especially useful is the capability
+to deal with PostGIS layers) to running complex and custom analyses through
+GRASS modules. Often is used to replace or integrate proprietary software, and
+several migrations have been accomplished or are underway, both in small and in
+large companies and public administrations. Among the hundreds of people that
+have attended courses on QGIS use, a common feeling is that the switch from
+proprietary software is painless, because many tasks and menus are very similar,
+and the interface is generally judged very intuitive. No doubt thanks to its
+free and open source licence, it is also used in some of the poorest countries,
+thus helping to reduce the world digital divide and bring more geoinformatic
+knowledge where local conditions are more difficult.
 Professional support is provided by several companies.
@@
 \\QGIS Blog: \url{http://blog.qgis.org}
-\\QGIS User Mailing List: \url{http://lists.osgeo.org/mailman/listinfo/qgis-user}
+\\QGIS User Mailing List:
+\url{http://lists.osgeo.org/mailman/listinfo/qgis-user}
 \\QGIS IRC: Channel \#qgis port 6667 at \url{irc.freenode.net}

### 2009-02-01 articles/2009/geoinformatics/article.tex
Added author details and some notes to 'who uses QGIS' section
git-svn-id: https://svn.osgeo.org/qgis/trunk@10087 c8812cc2-4d05-0410-92ff-de0c093fc19c

@@
 to deal with PostGIS layers) to running complex and custom analyses through
-GRASS modules. Often is used to replace or integrate proprietary software, and
+GRASS modules. Often QGIS is used to replace or integrate proprietary software, and
 several migrations have been accomplished or are underway, both in small and in
@@
 knowledge where local conditions are more difficult.
+
+QGIS is also used by many software developers to produce new GIS enabled
+applications. As a Free alternative to GIS toolkits such as ESRI ArcObjects,
+QGIS provides a compelling option. Yet more developers are building custom
+plugins to suit their own needs and are sharing them via plugin repositories.
+
+One of the curious aspects of being a Free and Open Source project is that we 
+have very little idea of exactly how many users we have. Since the software can 
+be freely copied and passed around after it is downloaded it is difficult to 
+judge useage numbers. With around 1550 registered users on our community map 
+we can extrapolate a user base in excess of 15000 given a conservative 
+estimate of a 1% sign up rate.
+
 Professional support is provided by several companies.
@@
 \\Gary Sherman <sherman@mrcc.com>
-\\Tim Sutton <tim@linfiniti.com>
+\\Tim Sutton <tim@linfiniti.com>: Tim runs a consultancy business in Gauteng,
+South africa where he provides commercial support and development services for
+QGIS and other FOSS GIS software.
 \\Marco Hugentobler <marco.hugentobler@karto.baug.ethz.ch>

### 2009-02-02 articles/2009/geoinformatics/article.tex
Added author background
git-svn-id: https://svn.osgeo.org/qgis/trunk@10089 c8812cc2-4d05-0410-92ff-de0c093fc19c

@@
 An example using this approach is the QGIS mapserver project
-(\url{http://karlinapp.ethz.ch}) that provides a WMS
+(\url{http://karlinapp.ethz.ch/qgis\_wms}) that provides a WMS
 compatible mapserver on top of the QGIS core library. This software has no 
@@
 QGIS and other FOSS GIS software.
-\\Marco Hugentobler <marco.hugentobler@karto.baug.ethz.ch>
+\\Marco Hugentobler <marco.hugentobler@karto.baug.ethz.ch>: Marco lives in Zurich, Switzerland.
+He works for the Institute of Cartography, ETH Zurich and for his company that provides programming and consulting services for FOSS GIS software.
 \\Paolo Cavallini <cavallini@faunalia.it>

### 2009-02-02 articles/2009/geoinformatics/article.tex
created images for the article and author information
git-svn-id: https://svn.osgeo.org/qgis/trunk@10092 c8812cc2-4d05-0410-92ff-de0c093fc19c

@@
    \caption{Quantum GIS 1.0.0 'Kore'}\label{fig:qgis10}\smallskip
-   \includegraphics[clip=true, width=12cm]{qgis10}
+   \includegraphics[clip=true, width=10cm]{qgis10}
 \end{center}
@@
    \begin{center}
-   \caption{QGIS Geoprocessing Tools}
-    \label{fig:geoprocessing}\smallskip
-   \includegraphics[clip=true, width=8cm]{geoprocessing}
+   \caption{Shapefile to PostGIS Import Tool}
+    \label{fig:spit}\smallskip
+   \includegraphics[clip=true, width=10cm]{spit}
 \end{center}
@@
     \label{fig:grass-plugin}\smallskip
-   \includegraphics[clip=true, width=14cm]{grass-plugin}
+   \includegraphics[clip=true, width=10cm]{grass-plugin}
 \end{center}
@@
    \caption{QGIS Python Plugin Installer}\label{fig:python-plugin}\smallskip
-   \includegraphics[clip=true, width=14cm]{python-plugin-installer}
+   \includegraphics[clip=true, width=10cm]{python-plugin-installer}
 \end{center}
@@
 
-Otto Dassau <dassau@nature-consult.de>
+Otto Dassau <dassau@nature-consult.de>: Otto lives in Hannover, Germany. His
+background is Open Source GIS and applied remote sensing. 
 \\Gary Sherman <sherman@mrcc.com>

### 2009-02-03 articles/2009/geoinformatics/article.tex
Added perspective/conclusion, hopefully not to heavy on the marketing...
git-svn-id: https://svn.osgeo.org/qgis/trunk@10097 c8812cc2-4d05-0410-92ff-de0c093fc19c

@@
 we can extrapolate a user base in excess of 15000 given a conservative 
-estimate of a 1% sign up rate.
+estimate of a 1\% sign up rate.
 
@@
 \subsection{Perspective / Conclusion}
+
+Quantum GIS began as a one-developer application that was met with skepticism
+by many asking ``Why another open source GIS?''. Although the initial goals
+were modest, QGIS has become a mature and extensible tool for viewing,
+editing, and performing GIS analysis. Creating a feature-complete GIS from
+scratch is a tremendous undertaking and at the outset was not really a goal of
+the project. With the GRASS integration and the extensibility possible through
+plugins, QGIS is positioned to grow into an even more robust toolset for the
+GIS user.
+
+Early in life, the QGIS community was small and grew quite slowly.
+With the addition of several key developers, the features and capabilities
+expanded rapidly and with it, the community. QGIS now has an established
+community providing peer support, testing, and new features via plugins.
+
+At version 1.0, QGIS provides a rich, stable API from which developers can
+create custom solutions in Python or C++. As the project moves forward, 
+there are many exciting developments underway in both the core application and
+plugins.
+
+While it took nearly 7 years to get to version 1.0, the process is a
+testimony to the power of open source in bringing the talents and ideas of
+many individuals together to create a tool used by thousands in academia,
+government, and private industry around the world.
 
@@
 background is Open Source GIS and applied remote sensing. 
-\\Gary Sherman <sherman@mrcc.com>
+\\Gary Sherman <gsherman@mrcc.com>: Gary lives and works in Alaska and been torturing computers and programming languages well over two decades. In 2002 he founded the Quantum GIS project. 
 \\Tim Sutton <tim@linfiniti.com>: Tim runs a consultancy business in Gauteng,

### 2009-02-03 articles/2009/geoinformatics/article.tex
Some spelling and grammar corrections and very minor formatting. Feel free to diff and adjust as you see fit. This completes my (gsherman) review.
git-svn-id: https://svn.osgeo.org/qgis/trunk@10098 c8812cc2-4d05-0410-92ff-de0c093fc19c

@@
 contributions are mainly on a voluntary basis, except in a few cases where 
-contributors are able to contribute to QGIS as part of their daily work. QGIS 
+people are able to contribute to QGIS as part of their daily work. QGIS 
 is managed by the Project Steering Committee (PSC), a five member committee
@@
 
-With community platforms such as our website, wiki, forums and blog the QGIS
-project
-provides current news, release, usage, and development information. In most
-cases 
-these community web sites permit user contributions after registering. 
-The QGIS-user mailing, forum and Internet Relay Chat (IRC) provide a valuable
-interface 
-with other users and for discussions of QGIS in general. In the spirit of open 
-process and sharing knowledge, contacting developers directly instead of going
-through 
-these community based avenues of communication is frowned upon.
+With community platforms such as the website, wiki, forums, and blog, the QGIS
+project provides current news, release, usage, and development information. In
+most cases these community web sites permit user contributions after
+registering.  The QGIS-user mailing, forum and Internet Relay Chat (IRC)
+provide a valuable interface with other users and for discussions of QGIS in
+general. In the spirit of open process and sharing knowledge, contacting
+developers directly instead of going through these community based avenues of
+communication is frowned upon.
 
@@
 Working with QGIS is simple and intuitive as you are presented with a
-modern and friendly graphical user interface (GUI) based on QT4. All
+modern and friendly graphical user interface (GUI) based on Qt4. All
 functions are clearly separated (see Figure~\ref{fig:qgis10}).
@@
 The \textbf{map overview} area provides a full extent view of selected layers
-with a rectangle showing the current map extent in the map view. And the
-\textbf{status bar} finally shows the current mouse pointer position in map
+with a rectangle showing the current map extent in the map view. And finally, the
+\textbf{status bar} shows the current mouse pointer position in map
 coordinates, view extents of the map view, the progress of rendering or
 analysis activities, the current map scale depending on the defined
-Coordinate Reference System (CRS) and information about available external
+Coordinate Reference System (CRS), and information about available external
 plugin updates.
@@
 
-QGIS offers a growing number of common GIS functionality provided by core
-features and plugins and at a glance provide following features:
+QGIS offers a growing array of common GIS functionality provided by core
+features and plugins, and at a glance provides following features:
 
@@
 \item compose print layouts adding map canvas, legend, scalebar, images and
-text lables in a print composer plugin;
+text labels in a print composer plugin;
 \item create, edit, manage and export vector layers into several formats.
@@
 
-Beside these two repositories a number of QGIS developers provide and maintain
+In addition to these two repositories, a number of QGIS developers provide and maintain
 their own repositories. These can be added to the repository list of the
@@
 \subsubsection{Development in the core classes of QGIS}
-Changes to existing classes may be submitted as patches using QGIS Project bug
+Changes to existing classes may be submitted as patches using the QGIS Project bug
 tracker (\url{https://trac.osgeo.org/qgis/}). The code maintainers of the QGIS
@@
 \subsubsection{Development of extensions as C++ or Python plugins}
-There is a plugin interface that allows extensions to access the running QGIS
+The plugin interface allows extensions to access the running QGIS
 instance and to use and extend the objects in the core of QGIS. Plugins may be
 written in C++ or in Python. The QGIS documentation contains simple examples
-for both programming languages making it straightforward to start with plugin 
-programming. The development of python plugins is especially fast and
-convenient. Simple plugins require only a few hours of development. As a result,
+for both programming languages, making it straightforward to get started with plugin 
+programming. The development of Python plugins is especially fast and
+convenient. Simple plugins require only a few hours of development time. As a result,
 an increasing number of users are contributing new plugins, of either
@@
 
-\subsubsection{Custom applications that use the QGIS libaries}
+\subsubsection{Custom applications that use the QGIS libraries}
 It is also possible to write new applications that provide their own user
@@
 
-An example using this approach is the QGIS mapserver project
+An example using this approach is the QGIS map server project
 (\url{http://karlinapp.ethz.ch/qgis\_wms}) that provides a WMS
-compatible mapserver on top of the QGIS core library. This software has no 
+compatible map server on top of the QGIS core library. This software has no 
 graphical user interface. It is a FastCGI application that waits until called
-by a webserver. It parses the request parameters and uses QGIS to render a map
-into an offscreen buffer. The content is then returned as binary image back to
+by a web server. It parses the request parameters and uses QGIS to render a map
+into an off-screen buffer. The content is then returned as a binary image back to
 the client.
@@
 laptops. The QGIS libraries offer the potential to be used as a GIS backend for 
-applications targeted to mobile devices.
+applications targeting mobile devices.
 
@@
 GRASS modules. Often QGIS is used to replace or integrate proprietary software, and
-several migrations have been accomplished or are underway, both in small and in
+several migrations have been accomplished or are underway, both in small and 
 large companies and public administrations. Among the hundreds of people that
@@
 QGIS is also used by many software developers to produce new GIS enabled
-applications. As a Free alternative to GIS toolkits such as ESRI ArcObjects,
-QGIS provides a compelling option. Yet more developers are building custom
+applications. As a free alternative to GIS toolkits such as ESRI ArcObjects,
+QGIS provides a compelling option. Even more developers are building custom
 plugins to suit their own needs and are sharing them via plugin repositories.
@@
 One of the curious aspects of being a Free and Open Source project is that we 
-have very little idea of exactly how many users we have. Since the software can 
+have very little idea of exactly how many people are using QGIS. Since the software can 
 be freely copied and passed around after it is downloaded it is difficult to 
-judge useage numbers. With around 1550 registered users on our community map 
-we can extrapolate a user base in excess of 15000 given a conservative 
+judge usage numbers. With around 1,550 registered users on the community map 
+we can extrapolate a user base in excess of 15,000 given a conservative 
 estimate of a 1\% sign up rate.
 
-Professional support is provided by several companies.
+Professional support for QGIS is provided by a number of companies whose
+services are listed on the project website.
 

### 2009-02-03 articles/2009/geoinformatics/article.tex
text is done and handed in
git-svn-id: https://svn.osgeo.org/qgis/trunk@10100 c8812cc2-4d05-0410-92ff-de0c093fc19c

@@
 
-Otto Dassau <dassau@nature-consult.de>: Otto lives in Hannover, Germany. His
-background is Open Source GIS and applied remote sensing. 
-\\Gary Sherman <gsherman@mrcc.com>: Gary lives and works in Alaska and been torturing computers and programming languages well over two decades. In 2002 he founded the Quantum GIS project. 
-\\Tim Sutton <tim@linfiniti.com>: Tim runs a consultancy business in Gauteng,
-South africa where he provides commercial support and development services for
-QGIS and other FOSS GIS software.
-\\Marco Hugentobler <marco.hugentobler@karto.baug.ethz.ch>: Marco lives in Zurich, Switzerland.
-He works for the Institute of Cartography, ETH Zurich and for his company that provides programming and consulting services for FOSS GIS software.
-\\Paolo Cavallini <cavallini@faunalia.it>
+Otto Dassau <dassau@nature-consult.de>: Otto lives and works in Hannover,
+Germany. His topics are FOSS GIS and applied remote sensing.
+\\Gary Sherman <gsherman@mrcc.com>: Gary lives and works in Alaska and been
+torturing computers and programming languages well over two decades. In 2002
+he founded the Quantum GIS project. 
+\\Tim Sutton <tim@linfiniti.com>: Tim runs a consultancy business in
+Gauteng, South africa where he provides commercial support and development
+services for QGIS and other FOSS GIS software.
+\\Marco Hugentobler <marco.hugentobler@karto.baug.ethz.ch>: Marco lives in
+Zurich, Switzerland. He works for the Institute of Cartography, ETH Zurich
+and for his company that provides programming and consulting services for
+FOSS GIS software.
+\\Paolo Cavallini <cavallini@faunalia.it>: Paolo lives and works in Italy. He
+heads a small and active group of professionals (biologists and agronomists)
+under the name Faunalia.
 
@@
 \\QGIS Blog: \url{http://blog.qgis.org}
-\\QGIS User Mailing List:
-\url{http://lists.osgeo.org/mailman/listinfo/qgis-user}
+\\QGIS User Mailing List: \url{http://lists.osgeo.org/mailman/listinfo/qgis-user}
 \\QGIS IRC: Channel \#qgis port 6667 at \url{irc.freenode.net}
 \\Open Source Geospatial Foundation: \url{http://www.osgeo.org}
+\\QGIS Map Server Project \url{http://karlinapp.ethz.ch/qgis\_wms}
+\\GNU GPL: \url{http://www.fsf.org/licensing/licenses/gpl.html}
+\\Open Source Geospatial Foundation: \url{http://www.osgeo.org}

### 2010-11-17 articles/2009/geoinformatics/article.tex

@@
 The \textbf{map overview} area provides a full extent view of selected layers
-with a rectangle showing the current map extent in the map view. And finally, the
+with a rectangle showing the current map extent in the map view. And finally,
+the
 \textbf{status bar} shows the current mouse pointer position in map
@@
 
-In addition to these two repositories, a number of QGIS developers provide and maintain
+In addition to these two repositories, a number of QGIS developers provide and
+maintain
 their own repositories. These can be added to the repository list of the
@@
 provides an assurance that plugins and applications developed against the 1.0
-API 
-will work against future releases in the 1.X release series.
+API will work against future releases in the 1.X release series.
 
 \subsubsection{Development in the core classes of QGIS}
-Changes to existing classes may be submitted as patches using the QGIS Project bug
+Changes to existing classes may be submitted as patches using the QGIS Project
+bug
 tracker (\url{https://trac.osgeo.org/qgis/}). The code maintainers of the QGIS
@@
 written in C++ or in Python. The QGIS documentation contains simple examples
-for both programming languages, making it straightforward to get started with plugin 
+for both programming languages, making it straightforward to get started with
+plugin 
 programming. The development of Python plugins is especially fast and
-convenient. Simple plugins require only a few hours of development time. As a result,
+convenient. Simple plugins require only a few hours of development time. As a
+result,
 an increasing number of users are contributing new plugins, of either
@@
 by a web server. It parses the request parameters and uses QGIS to render a map
-into an off-screen buffer. The content is then returned as a binary image back to
+into an off-screen buffer. The content is then returned as a binary image back
+to
 the client.
@@
 to deal with PostGIS layers) to running complex and custom analyses through
-GRASS modules. Often QGIS is used to replace or integrate proprietary software, and
+GRASS modules. Often QGIS is used to replace or integrate proprietary software,
+and
 several migrations have been accomplished or are underway, both in small and 
@@
 One of the curious aspects of being a Free and Open Source project is that we 
-have very little idea of exactly how many people are using QGIS. Since the software can 
+have very little idea of exactly how many people are using QGIS. Since the
+software can 
 be freely copied and passed around after it is downloaded it is difficult to 
@@
 FOSS GIS software.
-\\Paolo Cavallini <cavallini@faunalia.it>: Paolo lives and works in Italy. He
-heads a small and active group of professionals (biologists and agronomists)
-under the name Faunalia.
+\\Paolo Cavallini <cavallini@faunalia.it>: Paolo lives and works mostly in Italy. He
+provides commercial support for QGIS and other FOSS GIS through his companies
+Faunalia.it and Faunalia.pt, and promotes FOSS GIS through the non-profit
+GFOSS.it.
 

### 2010-11-20 src/plugins/globe/globe_plugin.cpp
added modal dialog

@@ -163,11 +163,13 @@ void GlobePlugin::settings()
 {
   QgsGlobePluginDialog* settingsDialog = new QgsGlobePluginDialog( mQGisIface->mainWindow(), QgisGui::ModalDialogFlags );
   settingsDialog->setAttribute( Qt::WA_DeleteOnClose );
-  settingsDialog->exec();
-  
-  //QMessageBox msgBox;
-  //msgBox.setText(settingsDialog->stereoMode);
-  //msgBox.exec();
+  if (settingsDialog->exec())
+  {
+    viewer.QgsGLWidgetAdapter::setStereoMode("ANAGLYPHIC");
+    //above works
+    //this second would be needed but causes a segmentation fault
+    //viewer.QgsGLWidgetAdapter::setStereoMode(settingsDialog->stereoMode);
+  }
 }
 
 void GlobePlugin::setupMap()

### 2010-11-20 src/plugins/globe/globe_plugin.cpp
refactoring of setStereoMode done

@@ -67,6 +67,7 @@ GlobePlugin::GlobePlugin( QgisInterface* theQgisInterface )
     mQActionSettingsPointer( NULL ),
     viewer(),
     mQDockWidget( tr( "Globe" ) ),
+    mSettingsDialog( theQgisInterface->mainWindow(), QgisGui::ModalDialogFlags ),
     mTileSource(0),
     mElevationManager( NULL ),
     mObjectPlacer( NULL )
@@ -161,14 +162,9 @@ void GlobePlugin::run()
 
 void GlobePlugin::settings()
 {
-  QgsGlobePluginDialog* settingsDialog = new QgsGlobePluginDialog( mQGisIface->mainWindow(), QgisGui::ModalDialogFlags );
-  settingsDialog->setAttribute( Qt::WA_DeleteOnClose );
-  if (settingsDialog->exec())
+  if (mSettingsDialog.exec())
   {
-    viewer.QgsGLWidgetAdapter::setStereoMode("ANAGLYPHIC");
-    //above works
-    //this second would be needed but causes a segmentation fault
-    //viewer.QgsGLWidgetAdapter::setStereoMode(settingsDialog->stereoMode);
+    viewer.QgsGLWidgetAdapter::setStereoMode(mSettingsDialog.stereoMode);
   }
 }
 
